%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Berufserfahrung}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\cventry
  {Performance \& Digital Automation Specialist}
  {Hermex Trade GmbH}
  {Schaffhausen, Schweiz}
  {Feb. 2024 - Heute}
  {
    \begin{cvitems}
\item {Engineered cross-platform automation workflows, integrating ERP, CRM, and e-commerce systems to streamline business processes and enhance scalability with low-code infrastructure.}
\item {Automated real-time price adjustments in online retail, eliminating manual intervention and optimizing promotional execution for increased revenue generation.}
\item {Developed AI-driven address verification and automatic dispatch approval systems, significantly reducing order errors and enhancing overall logistics efficiency.}
\item {Spearheaded the implementation of advanced tracking systems on web platforms, which boosted business intelligence and enriched user insights for strategic decision-making.}
\end{cvitems}
  }

\cventry
  {Digital Project Manager}
  {SiL Management \& Treuhand AG}
  {Freelance (Remote)}
  {Sept. 2023 - Heute}
  {
    \begin{cvitems}
\item {Implemented automated workflows that reduced manual invoice processing time by 70\%, enhancing operational efficiency.}
\item {Developed tailored web solutions with API integrations, eliminating manual data entry and significantly improving data accuracy.}
\item {Conducted comprehensive analysis of financial processes, identifying automation opportunities that streamlined administrative tasks.}
\item {Led digital transformation projects, managing stakeholder relationships and ensuring effective process documentation and technical execution.}
\end{cvitems}
  }

\cventry
  {System Administrator / Developer}
  {GF Piping Systems Schweiz}
  {Schaffhausen, Schweiz}
  {Aug. 2021 - Sept. 2023}
  {
    \begin{cvitems}
\item {Implemented a secure self-hosted password management platform with AES-256 encryption, centralizing and safeguarding sensitive data across the organization.}
\item {Designed a RSYNC-based update distribution system to efficiently deploy Java applications across 30+ logistics center clients, reducing startup delays and enhancing operational efficiency.}
\item {Developed and maintained mission-critical Java applications, streamlining cross-department business processes in a global organization with over 14,000 employees.}
\item {Led the development of a Linux server application for real-time data transfer to mobile devices, optimizing pallet and package handling processes in logistics.}
\end{cvitems}
  }

\cventry
  {Co-Founder \& Tech Lead – E-Commerce (Schuhhandel)}
  {Sneakzmarket GmbH}
  {Schaffhausen, Schweiz}
  {Apr. 2021 - Dez. 2023}
  {
    \begin{cvitems}
\item {Spearheaded the automation of all business processes, enhancing operational efficiency from product import to invoicing, resulting in substantial profit growth.}
\item {Engineered and maintained a scalable infrastructure, successfully migrating from WooCommerce to Shopify with seamless real-time inventory synchronization, ensuring uninterrupted operations.}
\item {Optimized customer experience and conversion rates through innovative web solutions, including automated image processing and enhanced page speed, leading to significant revenue increases.}
\item {Implemented data-driven analytics strategies to continuously refine performance, achieving and sustaining seven-figure revenue streams through targeted marketing efforts.}
\end{cvitems}
  }

\cventry
  {Application Engineer}
  {GF Piping Systems Schweiz}
  {Schaffhausen, Schweiz}
  {Aug. 2019 - Juli 2021}
  {
    \begin{cvitems}
\item {Spearheaded the deployment and maintenance of Windows and Linux servers in a hybrid infrastructure, enhancing support for critical business processes and internal development environments.}
\item {Optimized the logistics operations by managing print servers, configuring label printers, and rolling out drivers, ensuring cross-departmental reliability of printing processes.}
\item {Administered Active Directory across multiple locations and departments, leading to streamlined user management and enhanced permissions control with efficient implementation of group policies.}
\item {Implemented robust virtualization environments using VMware, including snapshot management and failover strategies, to ensure high availability and resource allocation for enterprise-critical services.}
\end{cvitems}
  }

\cventry
  {Platform Developer}
  {Curtiss-Wright Corp.}
  {Schaffhausen, Schweiz}
  {Aug. 2018 - Juli 2019}
  {
    \begin{cvitems}
\item {Spearheaded VLAN segmentation and routing strategies, enhancing data security and performance across corporate networks.}
\item {Led administration of Linux and Windows server environments, implementing regular updates and backups to ensure optimal system availability.}
\item {Developed robust security measures including firewall configurations and access control policies, aligning with corporate compliance standards.}
\item {Designed comprehensive system maintenance plans, incorporating patch management, monitoring, and incident response to boost operational efficiency.}
\end{cvitems}
  }

\cventry
  {IT Systems Specialist}
  {Wibilea AG}
  {Schaffhausen, Schweiz}
  {Aug. 2017 - Juli 2018}
  {
    \begin{cvitems}
\item {Engineered robust internal IT infrastructure by configuring VLANs and establishing basic firewall rules, enhancing network security and stability.}
\item {Automated routine administrative tasks using Bash and PowerShell scripts, streamlining processes such as log rotation and user management, which boosted operational efficiency.}
\item {Collaborated in cross-functional IT projects, contributing to setup, documentation, and testing, which facilitated smooth project execution and timely delivery.}
\item {Diagnosed and resolved complex issues in Windows and Linux environments, maintaining system integrity and minimizing downtime through proactive monitoring and documentation.}
\end{cvitems}
  }
\end{cventries}
