%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Berufserfahrung}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\cventry
  {Performance \& Digital Automation Specialist}
  {Hermex Trade GmbH}
  {Schaffhausen, Schweiz}
  {Feb. 2024 - Heute}
  {
    \begin{cvitems}
\item {Spearheaded platform-wide automation workflows, integrating ERP, CRM, e-commerce, and helpdesk systems on scalable low-code infrastructure to optimize and streamline business processes.}
\item {Automated data-driven dynamic pricing for online shops, enabling precise, timed promotions execution without manual intervention, and enhancing sales and operational efficiency.}
\item {Developed AI-driven address verification and automated shipping authorization systems, reducing incorrect deliveries and support workload while expediting logistics processes.}
\item {Optimized internal ticket management by implementing automated routing, cross-department collaboration, and real-time notifications, significantly reducing response and resolution times.}
\end{cvitems}
  }

\cventry
  {Digital Project Manager}
  {SiL Management \& Treuhand AG}
  {Freelance (Remote)}
  {Sept. 2023 - Heute}
  {
    \begin{cvitems}
\item {Analysierte und optimierte Buchhaltungs- und Verwaltungsprozesse, wodurch die Effizienz um über 30\% gesteigert und automatisierte Lösungen implementiert wurden.}
\item {Entwickelte und implementierte Workflows zur automatischen Verarbeitung und Verbuchung von Rechnungen, was zu einer Reduzierung der manuellen Fehler um 25\% führte.}
\item {Erstellte maßgeschneiderte Weblösungen und Integrationen, um manuelle Eingaben zu eliminieren und die Datenqualität signifikant zu verbessern.}
\item {Leitete Digitalisierungsprojekte in kleinen und mittleren Unternehmen mit Fokus auf effektives Stakeholder-Management und nahtlose technische Umsetzung.}
\end{cvitems}
  }

\cventry
  {System Administrator / Developer}
  {GF Piping Systems Schweiz}
  {Schaffhausen, Schweiz}
  {Aug. 2021 - Sept. 2023}
  {
    \begin{cvitems}
\item {Designed and maintained critical Java applications to digitize key business processes, enhancing efficiency for a company with over 14,000 employees.}
\item {Implemented a secure, self-hosted password management platform with AES-256 encryption, improving security by replacing decentralized methods.}
\item {Developed an RSYNC-based update system for Java applications across 30+ clients, optimizing load times and eliminating startup delays in logistic operations.}
\item {Automated system configuration and software distribution, reducing manual errors and accelerating deployments through scripting and version control.}
\end{cvitems}
  }

\cventry
  {Co-Founder \& Tech Lead – E-Commerce (Schuhhandel)}
  {Sneakzmarket GmbH}
  {Schaffhausen, Schweiz}
  {Apr. 2021 - Dez. 2023}
  {
    \begin{cvitems}
\item {Led the full technical development and operational strategy for Sneakzmarket GmbH, enhancing the e-commerce infrastructure, including WooCommerce and later Shopify, achieving a seven-figure revenue through holistic automation of business processes.}
\item {Spearheaded the migration of complex system landscapes from WooCommerce to Shopify, implementing real-time inventory synchronization and maintaining seamless operations across platforms, resulting in error-free live transitions.}
\item {Developed and implemented data-driven analytics and conversion strategies, improving performance metrics significantly by focusing on user experience and conversion rate optimization, contributing to sustained revenue growth.}
\item {Engineered a centralized order management system for multiple shops, introducing automated label creation, shipment tracking, and a robust plugin architecture, which streamlined operations and reduced processing time.}
\end{cvitems}
  }

\cventry
  {Application Engineer}
  {GF Piping Systems Schweiz}
  {Schaffhausen, Schweiz}
  {Aug. 2019 - Juli 2021}
  {
    \begin{cvitems}
\item {Implemented and maintained a hybrid server infrastructure with Windows and Linux servers supporting critical business processes and development environments.}
\item {Enhanced security and efficiency by developing a secure, self-hosted password management system using AES-256 encryption, improving password distribution and eliminating external vulnerabilities.}
\item {Optimized department-wide print processes by managing print servers and configuring label printers, ensuring cross-departmental reliability.}
\item {Administered complex Active Directory environments, including user management and policy governance across multiple locations, improving organizational structure and security.}
\end{cvitems}
  }

\cventry
  {Platform Developer}
  {Curtiss-Wright Corp.}
  {Schaffhausen, Schweiz}
  {Aug. 2018 - Juli 2019}
  {
    \begin{cvitems}
\item {Managed internal network infrastructure, ensuring secure and efficient data flow through advanced VLAN segmentation, routing strategies, and switch configuration.}
\item {Administered a mixed Linux and Windows server environment, leading updates, backups, and system availability assurance for enhanced enterprise operations.}
\item {Designed and implemented security measures, including firewall rules and access control policies, achieving compliance with internal standards and regulations.}
\item {Developed system maintenance strategies encompassing patch management and incident response processes, significantly improving system reliability and uptime.}
\end{cvitems}
  }

\cventry
  {IT Systems Specialist}
  {Wibilea AG}
  {Schaffhausen, Schweiz}
  {Aug. 2017 - Juli 2018}
  {
    \begin{cvitems}
\item {Developed and implemented automation scripts using Bash and PowerShell, enhancing efficiency in routine administrative tasks like log rotation and system monitoring.}
\item {Spearheaded the configuration of internal IT infrastructure, including VLAN setups and basic firewall rules, significantly improving network security and performance.}
\item {Collaborated on cross-functional IT projects, focusing on setup, documentation, and testing, which streamlined operational workflows by 20\%.}
\item {Acquired and applied practical experience in troubleshooting and resolving technical issues across Windows and Linux environments, improving system reliability and user satisfaction.}
\end{cvitems}
  }
\end{cventries}
